### 2013-12-01 manuscripts/reply/short-reply.tex
added content of main-reply.tex to short-reply.tex

@@

>>>>

%&<latex>
\documentclass[letterpaper,12pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{../utils/preamble.tex}
\input{../utils/macros.tex}

\newcommand{\msTitle}{Why you should not fix a biased model-choice method by
adding an additional dimension of model choice: A reply to Hickerson et al.
\xspace}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\doublespacing
\raggedright
\setlength{\parindent}{0.5in}
\begin{linenumbers}

\begin{titlepage}
    \begin{flushleft}
        \sffamily

        \MakeUppercase{\large\bfseries \msTitle}

        \vspace{12pt}
        \textbf{Running head:} \MakeUppercase{Approximate Bayesian model
        choice}

        \vspace{12pt}
        Jamie R.\ Oaks$^{1,2}$, Jeet Sukumaran$^{3}$, Jacob A.\
        Esselstyn$^{4}$, Charles W.\ Linkem$^{5}$, Cameron D.\
        Siler$^{6}$, and Rafe M.\ Brown$^{1}$

        \bigskip
        $^1$\emph{Department of Ecology and Evolutionary Biology,
            Biodiversity Institute,
            University of Kansas,
            Lawrence, Kansas 66045}\\[.1in]
        $^3$\emph{Department of Biology,
            Duke University,
            Durham, North Carolina 27708} \\[.1in]
        $^4$\emph{Museum of Natural Science,
            Louisiana State University,
            119 Foster Hall,
            Baton Rouge, Louisiana 70803}\\[.1in]
        $^5$\emph{Department of Biology,
            University of Washington,
            Seattle, Washington 98195}\\[.1in]
        $^6$\emph{Sam Noble Museum,
            Department of Biology,
            University of Oklahoma,
            Norman, Oklahoma 73072}\\[.1in]
        $^2$\emph{Corresponding author} (\href{mailto:joaks1@gmail.com}{\tt
        joaks1@gmail.com})\\

    \end{flushleft}
\end{titlepage}

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Recently, \citet{Oaks2012} presented a simulation-based
    assessment of the approximate Bayesian phylogeographical model choice
    method implemented in \msb, and found the method to lack robustness and
    power to detect temporal variation in divergences that are randomly
    distributed over relatively broad periods of evolutionary history.
    They conclude that a likely mechanism behind the bias toward models with
    few divergence events is the small marginal likelihoods of models with more
    divergence time parameters due to the integration over vast parameter space
    with low likeihood and high prior density that is imposed by broad uniform
    priors.
    \citet{Hickerson2013} have responded to this work, questioning the priors
    used by \citet{Oaks2012} and presenting an approximate Bayesian
    model-averaging approach that uses narrow, empirically informed uniform
    priors.
    \citet{Hickerson2013} use this method to re-analyze the empirical dataset
    of \citet{Oaks2012} comprised of 22 pairs of vertebrate populations from
    the Philippines, and conclude the model-averaging approach circumvents the
    issues revealed by \citet{Oaks2012} and yields robust inference of
    divergence models.
    Furthermore, they argue that the biases revealed by \citet{Oaks2012} are
    inherent to the inefficient rejection algorithm implemented in \msb, rather
    than a result of low marginal likelihoods of parameter-rich models.
    Here we discuss an error in the methodology of \citet{Hickerson2013} that
    renders some of their results invalid and the remainder difficult to
    interpret.
    Furthermore, we demonstrate that the approach of \citet{Hickerson2013} is
    biased toward models with less parameter space, which manifests in a strong
    tendency to sample predominantly from models that exclude the true values
    of the model's parameters.
    Our results suggest that their model-averaged results are dominated by
    models that likely exclude at least some of the true divergence times
    across the 22 pairs of Philippine vertebrates, which adds to the
    difficulty in interpreting their results.
    We also show the approach of \citet{Hickerson2013} is still biased toward
    inferring simultaneous divergences even when the true divergences are
    randomly distributed over millions of generations.
    Our results, coupled with those of \citet{Oaks2012}, strongly suggest that
    low marginal likelihoods of complex models is a primary cause of the bias
    of \msb toward models with less parameter space.
    We discuss ways to mitigate this bias without resorting to adding an
    additional dimension of model choice to the model or using questionable
    empirically informed uniform priors.

    \vspace{12pt}
    \noindent\textbf{KEY WORDS: Approximate Bayesian computation; Bayesian
        model choice; empirical Bayes}

}

\newpage

@@

\section*{Acknowledgments}
We thank the National Science Foundation for supporting this work (DEB
1011423).
J.\ Oaks was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.

\bibliography{../bib/references}
% \bibliography{references}

%% LIST OF FIGURES %%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\singlespacing

\renewcommand\listfigurename{Figure Captions}
\cftsetindents{fig}{0cm}{2.2cm}
\renewcommand\cftdotsep{\cftnodots}
\setlength\cftbeforefigskip{10pt}
\cftpagenumbersoff{fig}
\listoffigures

\end{linenumbers}

%% TABLES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\singlespacing

\input{reply-tables.tex}

\clearpage

%% FIGURES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\input{reply-figures.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SUPPORTING INFO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}

\singlespacing

% PUT MAIN TEXT CITATION HERE
{
\renewcommand{\refname}{\noindent\MakeUppercase{\LARGE\sffamily\upshape supporting information}}
\begin{thebibliography}{1}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\providecommand{\urlprefix}{URL }

\bibitem[{Oaks et~al.(2014)Oaks, Sukumaran, Esselstyn, Linkem, Siler, Brown,
  and Holder}]{Oaks2013reply}
Oaks, J.~R., J.~Sukumaran, J.~A.\ Esselstyn, C.~W.\ Linkem, C.~D.\ Siler,
    R.~M.\ Brown, and M.~T.\ Holder,
  % 2013.
\newblock \msTitle
% \newblock Evolution 67:991--1010.

\end{thebibliography}
}

\doublespacing
\input{reply-si-main.tex}

\newpage
\singlespacing

\input{reply-si-figures.tex}

\end{document}
